%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape MengLun Zhan} \\ \vspace{1pt}
    \small +886-978-631-625 $|$ \href{mailto:x@x.com}{\underline{aron0730@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{www.linkedin.com/in/menglunzhan}} %$|$
    %\href{https://github.com/...}{\underline{github.com/jake}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Taiwan University}{2019 -- 2022}
      {M.S. in Engineering Science}{Taipei, Taiwan}
    \resumeSubheading
      {National Taiwan Normal University}{2015 -- 2019}
      {B.S. in Electrical Engineering}{Taipei, Taiwan}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Wolley Tech}{Dec. 2024 -- Present}
      {Digital Verification Engineer}{}
      \resumeItemListStart
        \resumeItem{Spearheaded UVM-based verification of PCIe/CXL IPs, including environment bring-up, test planning, and coverage tracking.}
        \resumeItem{Developed scalable testbenches and reusable components across multiple projects, accelerating verification cycles.}
        \resumeItem{Partnered with cross-functional teams to debug complex protocol and timing issues using Verdi and Synopsys VIP.}
      \resumeItemListEnd

    \resumeSubheading
      {Wolley Tech}{Jun. 2023 -- Dec. 2024}
      {Firmware Engineer}{}
      \resumeItemListStart
        \resumeItem{Implemented SSD firmware features including FTL, HMB, TRIM, and RAM disk for performance and reliability.}
        \resumeItem{Optimized memory usage via LRU-based allocators and custom storage algorithms.}
        \resumeItem{Developed Python tools for test automation, serial parsing, and validation support.}
        \resumeItem{Contributed to PCIe Root Port bring-up, including BAR setup and AER error handling.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{PCIe Root Complex integrate Endpoint} $|$ \emph{UVM , AMBA Integration, Scoreboard Design}}{2025}
      \resumeItemListStart
        \resumeItem{Verified Root Complex integrating endpoints with ECAM, Type0/1 routing, and AXI/AHB/APB interconnects.}
         \resumeItem{Built the UVM environment, including interface bindings, agent connections, and reusable base sequences.}
        \resumeItem{Developed APB configuration sequences, AHB adapter and integrated into the UVM testbench.}
        \resumeItem{Built reusable scoreboard to validate MMIO transactions, reducing debug time and catching ordering bugs early.}
        \resumeItem{Led scenario planning and test case development, achieving 90\% coverage of ECAM and BAR configuration.}
        \resumeItem{Reduced verification time by 25\% by modularizing test components and introducing reusable base sequences.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{PCIe Switch IP} $|$ \emph{Legacy UVM Extension, Scenario Test Design, AXI-to-PCIe Flow}}{2025}
      \resumeItemListStart
        \resumeItem{Verified a multi-port PCIe Switch with upstream (USP) and downstream (DSP) ports supporting peer-to-peer traffic and AXI interfaces.}
        \resumeItem{Enhanced legacy UVM environment and created testcases simulating TLP forwarding, AXI burst handling, and protocol violations.}
        \resumeItem{Achieved 95\% functional coverage and 100\% assertion pass rate across multiple traffic scenarios.}
        \resumeItem{Traced and resolved 20+ critical bugs using waveform analysis (Verdi) and transaction-level protocol tracing.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{CXL Controller} $|$ \emph{UVM, TLP Monitor, Scoreboard Architecture, PCIe/CXL Compliance}}{2025}
      \resumeItemListStart
        \resumeItem{Designed and implemented a TL RX's monitor and scoreboard to verify TLP decoding accuracy, protocol compliance, and format consistency per PCIe/CXL spec.}
        \resumeItem{Built a parameterizable reference model to reconstruct TLPs from configurable bus slices, handling endian conversion and field decoding.}
        \resumeItem{Developed a compare engine to validate format/type, length, prefix presence, and header/payload integrity.}
        \resumeItem{Added error classification logic and automated reporting to detect mismatches with precise root cause labeling.}
        \resumeItem{Instrumented coverage hooks across 50+ TLP variations, boosting decoding and ordering coverage by 30\%.}
        \resumeItem{Enabled early-stage functional debug and reduced triage time by implementing cross-layer tracing between Data Link and Transaction Layers.}
      \resumeItemListEnd



  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: SystemVerilog, Verilog, C, C++, Python} \\
     \textbf{Protocols}{: PCIe, AXI, AHB, APB, CXS} \\
     \textbf{Tools}{: VCS, Verdi, Synopsys VIP, Git, Perforce, Jenkins, Jira} \\
     \textbf{Methodologies}{: UVM, Environment Component Design, Functional Coverage, RAL}
    }}
  \end{itemize}


%-------------------------------------------
\end{document}

%https://www.overleaf.com/